### 2019-05-29 doc/chapters/towards_verifying_addition.tex
case object

\section{Rewriting Generics}
// I dont understand this.. maybe just a missing feature in Stainless?
Stainless output:
\begin{lstlisting}
  [ Error  ] NumberType.scala:3:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]

\end{lstlisting}

\begin{lstlisting}[language=scala]
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

\section{Rewriting Objects}
// TODO reason?

Stainless output:
\begin{lstlisting}
[ Error  ] CurrencyUnits.scala:54:1: Objects cannot extend classes or implement
           traits, use a case object instead
           object Satoshis extends BaseNumbers[Satoshis] {
\end{lstlisting}

Changing the objects that extends classes to case objects solves this problem.

>>>>

\section{Rewriting Generics}
// I dont understand this.. maybe just a missing feature in Stainless?
Stainless output:
\begin{lstlisting}
  [ Error  ] NumberType.scala:3:30: Unknown type parameter type T
             sealed abstract class Number[T <: Number[T]]
\end{lstlisting}

This is a missing feature in Stainless.
\begin{lstlisting}[language=scala]
  sealed abstract class Number[T <: Number[T]] extends BasicArithmetic[T]  
\end{lstlisting}

\section{Rewriting Objects}
Stainless output:
\begin{lstlisting}
[ Error  ] CurrencyUnits.scala:54:1: Objects cannot extend classes or implement
           traits, use a case object instead
           object Satoshis extends BaseNumbers[Satoshis] {
\end{lstlisting}

Changing the objects that extends classes to case objects solves this problem.
This is, due to the internal design of Scala and Java.
It's possible to reason about a case object but not about an object.
This needs a fundamental knowledge of Scala and some functional paradigms that should not be part of this thesis.
The issue \mypound520 on Stainless GitHub gives some thoughts about this.
